Solving Collective Spin Hamiltonians with Decoherence

### 2018-10-03 soc_squeezing/cumulant_expansions.tex
fixed error in combinatorial factor and modified some text

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} \sum_{\p{\v\rho;\v r}}
  \sum_{\p{\v\ell;\v m,\v n,\v r,\v\rho}}
  f_{\v m\v n\v r} g_{\v\rho} \v\eta_{\v\rho} c_{\v\ell\v\rho} P_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where the sums over $\p{\v\rho;\v r}$ and
$\p{\v\ell;\v m,\v n,\v r,\v\rho}$ respectively denote sums over all
values of $\v\rho$ and $\v\ell$ with the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \abs{\set{\ell^\mu_a}}
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu,
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv { N - \abs{\v\ell} \choose \sum_{\mu,\nu}\rho^{\mu\nu}_0},
\end{align}
with $\abs{\v\ell}$ equal to the number of elements in $\v\ell$,
accounts for the multiplicity of terms which are equivalent up to a
permutation of indices involving the identity operators in
\eqref{eq:Q_K_rho_simp}.

@@

The sums in \eqref{eq:SS_simp} generally involve a large number of
terms; in practice, many of these terms will be equal to zero.  We
can, however, impose additional restrictions on these sums in such a
way as to throw out terms which vanish, and keep those which do not.
Remembering that $s$ counts the number of spins which are addressed by
both operators $P_{\v j}$ and $P_{\v k}$ in \eqref{eq:SS_PP}, the
first restriction we can impose comes from recognizing that for given
$\S_{\v m},\S_{\v n}$, the overlap $s$ is bounded as
\begin{align}
  \max\set{0,\sum_\mu\p{m_\mu+n_\mu}-N}
  \le s \le \min\set{N,\sum_\mu\p{m_\mu+n_\mu}}.
\end{align}
In addition, the multiplication table $\eta_{\mu\nu\kappa}$ may
generally contain zeros that we can preemptively avoid with
restrictions on $\v r$ and $\v\rho$.  Recalling that $r_{\mu\nu}$
counts the number of operators addressed by
$\sigma_\mu\sigma_\nu=\sum_\kappa\eta_{\mu\nu\kappa}\sigma_\kappa$, if
$\eta_{\mu\nu\kappa}=0$ for all $\kappa$,
i.e.~$\sigma_\mu\sigma_\nu=0$, then any term with $r_{\mu\nu}>0$ will
vanish.  Our second restriction on the sums in \eqref{eq:SS_simp} is
therefore to fix $r_{\mu\nu}=r_{\nu\mu}=0$ for all $\mu,\nu$ with
$\sigma_\mu\sigma_\nu=0$.  Finally, we can avoid the nullifying effect
of any additional zeros in the multiplication table
$\eta_{\mu\nu\kappa}$, which will appear in $\v\eta_{\v\rho}$ as
defined in \eqref{eq:eta_rho}, by restricting $\rho^{\mu\nu}_\kappa=0$
for all $\mu,\nu,\kappa$ with $\eta_{\mu\nu\kappa}=0$.  These
restrictions are sufficient to ensure that all individual terms in
\eqref{eq:SS_simp} are nonzero, although they do not rule out the
possibility of several terms canceling out.

>>>>

We have now simplified $Q_{\v K}$ sufficiently to substitute it back
into \eqref{eq:SS_PQ}, which (removing the tilde from $\tilde{\v\rho}$
to simplify notation) gives us
\begin{align}
  \S_{\v m} \S_{\v n}
  = \sum_{s\ge0} \sum_{\p{\v r;\v m,\v n,s}} \sum_{\p{\v\rho;\v r}}
  \sum_{\p{\v\ell;\v m,\v n,\v r,\v\rho}}
  f_{\v m\v n\v r} g_{\v\rho} \v\eta_{\v\rho} c_{\v\ell\v\rho} P_{\v\ell},
  \label{eq:SS_simp}
\end{align}
where the sums over $\p{\v\rho;\v r}$ and
$\p{\v\ell;\v m,\v n,\v r,\v\rho}$ respectively denote sums over all
values of $\v\rho$ and $\v\ell$ with the restrictions
\begin{align}
  \sum_{\kappa} \rho^{\mu\nu}_\kappa = r_{\mu\nu},
  &&
  \abs{\set{\ell^\mu_a}}
  = m_\mu + n_\mu - \sum_\kappa \p{r_{\mu\kappa}+r_{\kappa\mu}}
  + \sum_{\alpha,\beta} \rho^{\alpha\beta}_\mu,
\end{align}
and the combinatorial factor
\begin{align}
  c_{\v\ell\v\rho}
  \equiv \p{ N - \abs{\v\ell} }_ {\sum_{\mu,\nu}\rho^{\mu\nu}_0},
\end{align}
with $\abs{\v\ell}=\sum_\mu\p{m_\mu+n_\mu}-s$ equal to the number of
elements in $\v\ell$, accounts for the multiplicity of terms which are
equivalent up to a permutation of indices involving the identity
operators in \eqref{eq:Q_K_rho_simp}.

@@

The sums in \eqref{eq:SS_simp} generally involve a large number of
terms; in practice, many of these terms will be equal to zero.  We
can, however, impose additional restrictions on these sums in such a
way as to throw out terms which vanish, and keep those which do not.
Remembering that $s$ counts the number of spins which are addressed by
both operators $P_{\v j}$ and $P_{\v k}$ in \eqref{eq:SS_PP}, the
first restriction we can impose comes from recognizing that for given
$\S_{\v m},\S_{\v n}$, the overlap $s$ is bounded as
\begin{align}
  \max\set{0,\sum_\mu\p{m_\mu+n_\mu}-N}
  \le s \le \min\set{N,\sum_\mu\p{m_\mu+n_\mu}}.
\end{align}
In addition, the multiplication table $\eta_{\mu\nu\kappa}$ may
generally contain zeros that we can preemptively avoid with
restrictions on $\v r$ and $\v\rho$.  Recalling that $r_{\mu\nu}$
counts the number of operators addressed by
$\sigma_\mu\sigma_\nu=\sum_\kappa\eta_{\mu\nu\kappa}\sigma_\kappa$, if
$\eta_{\mu\nu\kappa}=0$ for all $\kappa$,
i.e.~$\sigma_\mu\sigma_\nu=0$, then any term with $r_{\mu\nu}>0$ will
vanish.  Our second restriction on the sums in \eqref{eq:SS_simp} is
therefore to fix $r_{\mu\nu}=r_{\nu\mu}=0$ for all $\mu,\nu$ with
$\sigma_\mu\sigma_\nu=0$.  Finally, we can avoid the nullifying effect
of any additional zeros in the multiplication table
$\eta_{\mu\nu\kappa}$, which appear as factors in
$\v\eta_{\v\rho}\propto\p{\eta_{\mu\nu\kappa}}^{\rho^{\mu\nu}_\kappa}$
as defined in \eqref{eq:eta_rho}, by restricting
$\rho^{\mu\nu}_\kappa=0$ for all $\mu,\nu,\kappa$ with
$\eta_{\mu\nu\kappa}=0$.  These restrictions are sufficient to ensure
that all individual terms in \eqref{eq:SS_simp} are nonzero, although
they do not rule out the possibility of several terms canceling out.
